Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
Simplify index scheme def, fix s_I def

\begin{definition}[Array subscripts and indices]
  An \emph{array subscript}, denoted $a(\bar{e})$, is an expression
  which reads from an array $a$ at an \emph{index} specified by a
  comma-separated sequence of integer expressions denoted $\bar{e}$ or
  in expanded form as $(e_1, \ldots, e_n)$. An index $\bar{e}$
  is called \emph{relative} if each $e \in \bar{e}$ involves an induction
  variable.

@@

Indexing schemes give an abstract
representation of array subscripts in the source language.
Our model represents the meaning of stencil specifications
as indexing schemes, which explain the range of possible
indexing behaviours which are consistent with the specification.
The relationship between source language
terms and indexing terms
 is given precisely by the following function \textsf{schematic},
 which forms part of checking and inference (\S\ref{sec:analysis}).

\newcommand{\schemeOne}{\textsf{s}_I}
%\newcommand{\schemeOne}{\textsf{schema$^1_I$}}
\newcommand{\schemeN}{\textsf{schematic}_I}
%\newcommand{\schemeN}{\textsf{schema$^n_I$}}
\begin{definition}%[Schematic]
\label{def:schematic}
Let $\schemeOne$ be a partial function, parameterised by a set of
induction variables $I$, mapping expression syntax to
$\domainVal$ values:
%%
\begin{align*}
\schemeOne(e)
 & =  \begin{cases}
c & e \equiv i + c \;\; \wedge \;\; i \in I \\
-c & e \equiv i - c \;\; \wedge \;\; i \in I \\
\infty & \textit{$I \not\subseteq \textit{FV}(e)$} \\
\bot   & \textit{otherwise}
\end{cases}
\end{align*}
where $\textit{FV}(e)$ is the set of free variables in $e$. In the
first two cases, expressions that are a constant offset of an
induction variable (\ie{}, neighbourhood indices) are mapped to the
offset $c$ or $-c$ $\in \domainVal$. In the third case, if the
expression is not a neighbourhood index, but neither is it a relative
index (\ie{}, it is not defined in terms of an induction variable) then it
is mapped to $\infty \in \domainVal{}$. Otherwise, $\schemeOne(e)$
is undefined (returns $\bot$).

>>>>

\begin{definition}[Array subscripts and indices]
  An \emph{array subscript}, denoted $a(\bar{e})$, is an expression
  which reads from an array $a$ at an \emph{index} specified by a
  comma-separated sequence of integer expressions denoted $\bar{e}$ or
  in expanded form as $(e_1, \ldots, e_n)$. An index $e_i$
  is called \emph{relative} if the expression involves an induction
  variable.

@@

Indexing schemes give an abstracts array subscripts.
Our model represents the meaning of stencil specifications
as indexing schemes, which explain the range of possible
indexing behaviours which are consistent with the specification.
The relationship between source language
terms and indexing terms
 is given precisely by the following function \textsf{schematic},
 which forms part of checking and inference (\S\ref{sec:analysis}).

\newcommand{\schemeOne}{\textsf{s}_I}
%\newcommand{\schemeOne}{\textsf{schema$^1_I$}}
\newcommand{\schemeN}{\textsf{schematic}_I}
%\newcommand{\schemeN}{\textsf{schema$^n_I$}}
\begin{definition}%[Schematic]
\label{def:schematic}
Let $\schemeOne$ be a partial function, parameterised by a set of
induction variables $I$, mapping expression syntax to
$\domainVal$ values:
%%
\begin{align*}
\schemeOne(e)
 & =  \begin{cases}
c & e \equiv i + c \;\; \wedge \;\; i \in I \\
-c & e \equiv i - c \;\; \wedge \;\; i \in I \\
\infty & \textit{$I \cap \textit{FreeVariables}(e) = \emptyset $} \\
\bot   & \textit{otherwise}
\end{cases}
\end{align*}
In the
first two cases, expressions that are a constant offset of an
induction variable (\ie{}, neighbourhood indices) are mapped to the
offset $c$ or $-c$ $\in \domainVal$. In the third case, if the
expression is not a neighbourhood index, but neither is it a relative
index (\ie{}, it is not defined in terms of an induction variable) then it
is mapped to $\infty \in \domainVal{}$. Otherwise, $\schemeOne(e)$
is undefined (returns $\bot$).
